---
title: "BA OL Retail Analytics"
author: "Sai Supriya Vengala"
date: "10/23/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r}
#Required libraries are to be loaded first
library(readr)
library(dplyr)
Online_Retail <- read_csv("Online_Retail.csv")
```


```{r}
#task1: calculating the countries accounting for more than 1% of the total transactions.
trans_country <-table(Online_Retail$Country)
transaction_percent<- round(100*prop.table(trans_country))
percentage <- cbind(trans_country, transaction_percent)
account <-subset(percentage, transaction_percent >1)
account
```
#task2:Creating  a  new  variable  ‘TransactionValue’  that  is  the  product  of  the  exising 
#‘Quantity’  and  ‘UnitPrice’ variables.
```{r}

TransactionValue <-Online_Retail$Quantity * Online_Retail$UnitPrice
Online_Retail <- Online_Retail %>% mutate(TransactionValue)
summary(Online_Retail$TransactionValue)

```
#task3:Calculating the countries with total transaction exceeding 130,000 British Pound
```{r}
Sum_trans <- sum(TransactionValue)
store<-summarise(group_by(Online_Retail, Country), Sum_trans)
Total <- filter(store, Sum_trans >130000)
Total
```
#task4
```{r}

Temp=strptime(Online_Retail$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
Online_Retail$New_Invoice_Date <- as.Date(Temp)
Diff <- Online_Retail$New_Invoice_Date[20000]- Online_Retail$New_Invoice_Date[10]
Diff
Online_Retail$Invoice_Day_Week= weekdays(Online_Retail$New_Invoice_Date) 
Online_Retail$New_Invoice_Hour = as.numeric(format(Temp, "%H"))
Online_Retail$New_Invoice_Month = as.numeric(format(Temp, "%m"))
```
#a)Showing the percentage of transactions (by numbers) by 
#days of the week  
 
```{r}

country_totaltran1<-summarise(group_by(Online_Retail,Invoice_Day_Week) ,Trans_val=n_distinct(InvoiceNo))
percentage1<-mutate(country_totaltran1,
                    Trans_perc=(Trans_val/sum(Trans_val))*100)
percentage1
```
#b) Showing  the  percentage  of  transactions  
#(by  transaction  volume)  by  days  of  the  week 
```{r}
country_tran1<-summarise(group_by(Online_Retail,Invoice_Day_Week),Trans_val1=sum(TransactionValue))
percen1<-mutate(country_tran1,Trans_perc1=(Trans_val1/sum(Trans_val1))*100)
percen1

```
#c)Show the percentage of transactions (by transaction volume)
#by month of the year
```{r}

country_totaltran2<-summarise(group_by(Online_Retail,New_Invoice_Month),Trans_val2=sum(TransactionValue))
percentage2<-mutate(country_totaltran2,Trans_perc2=(Trans_val2/sum(Trans_val2))*100)
percentage2
```
#d) The date with the highest number of transactions from Australia.
```{r}

Online_Retail %>% filter(Country == 'Australia') %>% group_by(New_Invoice_Date) %>% 
  summarise(max=max(TransactionValue))
```
#e)Calculating the hour of the day to start this so that the distribution is at 
#minimum for the customers?
```{r}
library(zoo)
start1<-summarise(group_by(Online_Retail,New_Invoice_Hour),
                  Tran_mini=n_distinct(InvoiceNo))
start1<-filter(start1,New_Invoice_Hour>=7&New_Invoice_Hour<=20)
start2<-rollapply(start1$Tran_mini,3,sum)
start3<-which.min(start2)
start3
```
#task5:Plotting the histogram of transaction values from Germany. Using the hist() function to plot.
```{r}

German_Trans <- subset(Online_Retail$TransactionValue, Online_Retail$Country =="Germany")
hist(German_Trans, xlim = c (-600, 900), breaks = 100, xlab = "transaction values of Germany", 
     main = "Germany")
```
#task6:Calculating the customer with highest number of transactions most valuable customer.
#(i.e. highest total sum of transactions)
```{r}
High_Trans <- na.omit(Online_Retail)
High_Trans <- summarise(group_by(Online_Retail, CustomerID), sum2 = sum(TransactionValue))
High_Trans[which.max(High_Trans$sum2),]
store1 <- table(High_Trans$CustomerID)
store1 <- as.data.frame(store1)
Val_Cust <- store1[which.max(store1$Freq),]
Val_Cust
```
#task7:Calculating  the  percentage  of  missing  values  for  each  variable  in  the  dataset  
```{r}
Miss_Val <-colMeans(is.na(Online_Retail)*100)
Miss_Val
```
#task8:Calculating the number of transactions with missing CustomerID records by countries?
```{r}
Val_Cust <- Online_Retail %>% filter(is.na(CustomerID)) %>% group_by(Country)
summary(Val_Cust$Country)
```
#task9:Calculating how often the costumers 
#comeback to the website for their next shopping

```{r}
Freaq <- Online_Retail %>%
  group_by(InvoiceNo, CustomerID, Country, New_Invoice_Date, New_Invoice_Month, New_Invoice_Hour, 
           Invoice_Day_Week) %>%
  summarise(Trans6 = sum(TransactionValue)) %>%
  mutate(Freq1 = Sys.Date() - New_Invoice_Date) %>%
  ungroup()
Freaq$Freq1 <- as.character(Freaq$Freq1)
Freaq$Freq2 <- sapply(Freaq$Freq1, 
  FUN = function(x) {strsplit(x, split = '[ ]')[[1]][1]})
Freaq$Freq2 <- as.integer(Freaq$Freq2)
head(Freaq, n = 5)
attach(Freaq)
FreaqCust <- Online_Retail %>%
  group_by(CustomerID, Country) %>%
  summarise(Cust_order = n_distinct(InvoiceNo),
            Trans7 = sum(TransactionValue), 
  PerDay = names(which.max(table(Invoice_Day_Week))), 
PerHour=names(which.max(table(New_Invoice_Hour))),
            Frequency = min(Freaq$Freq2))%>%
  ungroup()
head(FreaqCust)
```
#task10:Calculating the return rate for the French customers.
```{r}
France_Trans <- filter(Online_Retail, Country=="France")
Trow <- nrow(France_Trans)
Cancel_Trans <- nrow(subset(France_Trans,TransactionValue<0))
Cancel_Trans
No_Cancel<- Trow-Cancel_Trans
No_Cancel
Return=(Cancel_Trans/8556)
Return
```
#task11:Calculating the product that has generated the highest revenue for the retailer. 
#(i.e. item with the highest total sum of ‘TransactionValue’).
```{r}
TransactionValue <- tapply(Online_Retail$TransactionValue, Online_Retail$StockCode, sum)
TransactionValue[which.max(TransactionValue)] # to find highest value
```
#task12:Finding the unique customers that are represented in the dataset using unique() function
```{r}
Unique_Cust  <- unique(Online_Retail$CustomerID)
length(Unique_Cust )
```




